### 2023-02-24 paper-reviews/papers-2023.tex
Add reference to CPU top down analysis

>>>>

\section*{Performance}
\begin{itemize}
    \item \cite{Yasin:TopDownCPUPerfAnalysis:2014}:

    The paper proposes a top down performance analysis method for superscalar out-of-order processors. The paper discusses a couple of challenges for low-level CPU performance analysis; problems and limitation of the existing methods. The paper suggest a tree-like structure for the analysis. The top level of the hierarchy includes front end, bad speculations, retiring and frontend. Looking at specific part of the hierarchy allows to disregard events happening at other parts thus narrowing down the problem while moving to the leaves of the hierarchy. The author presented few usage examples of the methods and proposed changes to Intel's performance monitoring unit architecture.
\end{itemize}
